Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-06-19 tex/paper1/paper1.tex
edits to the paper; analysis program now displays posterior means

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  \cite{2003ApJ...595L..63D} show that TRACE
171\AA\ (TRansition Region And Coronal Explorer) time-series of bright
upper transition region emission above active region plage (also known
as moss) is a source of wavelet power. Periods of significant wavelet
power are found in the range 200 to 600 seconds, and typically persist
for 4–7 cycles.  Later work by \cite{2005ApJ...624L..61D} suggested
that spicule flux tubes tilted with respect to the solar surface
provide a mechanism by which oscillatory power from lower in the
atmosphere may be channeled to upper portions of the atmosphere.  This
suggests that a second model $M_{2}$ for the \Fps\ in regions should
be considered.  The second model $M_{2}$ has two contributions to the
overall \Fps; a background power-law of the form of $P_{1}$, and a
contribution that is more localized, $G(\nu)$.  The model is given by
\begin{equation}
\label{eqn:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\delta^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions (Figure
\ref{fig:fit171193}), and compared to decide which model best
describes the data. The details of the model fitting process are
described in \ref{sec:app:ind}.  The position of $G(\nu)$ is
restricted by permitting $\beta$ to vary in the range $1-10$ mHz only.
This restriction, which is imposed in the fitting process (see Section
\ref{{sec:app:ind}), arises from the observations of significant
  wavelet power in the period rangs 200 - 600 seconds as found by
  \cite{2003ApJ...595L..63D}.

@@

\subsection{Model fitting and selection}
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.  A
Bayesian/Markov chain Monte Carlo package (PyMC version 2.3,
\cite{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
the Bayesian posterior and determine model parameter estimates and
their uncertainty.  If $P_{i,j}$ is the power at Fourier frequency
$\nu_{j}$ from Model $i$ then the likelihood $L$ is
\begin{equation}\label{eqn:likelihood}
L = \prod_{j=1}^{N_{f}}
\frac{1}{\sqrt(2\pi\sigma^{2}}
\exp\left(
-\frac{(P_{i,j} - D_{j})^{2}}{2\sigma_{j}^{2}}
\right)
\end{equation}
where $D_{j}$ is the observed \mFps\ at frequency $\nu_{j}$,
$N_{f}$ is the number of Fourier frequencies, and $\sigma_{j}$ is the
normal distribution width at frequency $\nu_{j}$ .  Each of the priors for
the parameters in each model has a uniform distribution, and are given
in Table \ref{tab:priors}.  Each MCMC chain that was run took 100,000
samples, with burn-in assumed to be at 50,000 samples.  The chain is
thinned by taking every fifth element in the chain, forming the final
sample from which the parameter estimates and their uncertainties are
calculated.
\begin{deluxetable}{cc}
\tabletypesize{\scriptsize} 
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{Priors for each of the parameters used in Model 1
  (Equation \ref{eqn:pwrlaw}) and
  Model 2 (Equation \ref{eqn:pwrlawbump}) \label{tab:priors}}
\tablehead{
\colhead{Model 1} &
\colhead{Model 2} \\
}
\startdata
$A$ & $4.5 \times 10^-5 \rightarrow 22026$ &  $4.5 \times 10^-5 \rightarrow 22026$\\
$n$  &  $-1\rightarrow 6$   & $-1\rightarrow 6$  \\
$C$ & $2.1 \times 10^-9 \rightarrow 22026$  & $2.1 \times 10^-9 \rightarrow 22026$  \\
$\alpha$  & not applicable & $2.1 \times 10^-9 \rightarrow 148$ \\
$\beta$ & not applicable  & $1 - 10$ \\
$\delta$ & not applicable & $0.001\rightarrow 3$ \\
\enddata
\end{deluxetable}

@@

\begin{enumerate}
\item The MCMC sampler is run to fit Model 1, assuming $\sigma_{j} =
  \sigma_{original, j}$ the width of the distribution of Fourier power
  at frequency $G(\nu_{j})$.  Since these widths are much larger than
  $\sigma_{mean}$ is much wider than the standard error in the mean,
  it allows the fitting algorithm to converge to an approximate fit
  solution.
\item The MCMC sampler is run to fit Model 1 with $\sigma_{j} =
  \sigma_{mean, j}$, with $\sigma_{mean, j}= \sigma_{original,
    j}/sqrt{N_{eff}}$, seeded with estimated parameter values from
  step 1.  This generates a better estimate to the parameters of the
  model fit.  The resulting parameter estimates are given by the mean
  values of marginal probability distribution functions, and are the
  final estimates for Model 1.
\item The residuals of the model 1 fit to the data are then used to
  estimate the model parameters of $G(\nu)$.  This is done by
  (least-squares) fitting $G(\nu)$ to the positive residuals in the
  frequency range 0.1 - 1 mHz.
\item The MCMC sampler is run to fit Model 1,2assuming $\sigma_{j} =
  \sigma_{original, j}$, seeded with the mean parameter values of
  Model 1 from step 2 and the estimated $G(\nu)$ model parameters from
  step 3.
\item The MCMC sampler is run to fit Model 2 with $\sigma_{j} =
  \sigma_{mean, j}$, seeded with estimated parameter values from step
  4.  The resulting parameter estimates are given by the mean values
  of marginal probability distribution functions, and are the final
  estimates for Model 2.
\end{enumerate}
Models are selected using the Akaike and Bayesian Information Criteria
\citep{2007MNRAS.377L..74L}.  Conveniently, these quantities are also
calculated by the PyMC package used to perform the MCMC sampling.  The
68\% credible intervals for the parameters are quoted in Table
\ref{tab:parameters}.  The upper and lower limits to the credible
intervals are found by determining the values beyond which 16\% of the
probability lies in each wing of the marginal distributions.

@@

Give an idea of how the errors are found

>>>>

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  \cite{2003ApJ...595L..63D} show that TRACE
171\AA\ (TRansition Region And Coronal Explorer) time-series of bright
upper transition region emission above active region plage (also known
as moss) is a source of wavelet power. Periods of significant wavelet
power are found in the range 200 to 600 seconds, and typically persist
for 4–7 cycles.  Later work by \cite{2005ApJ...624L..61D} suggested
that spicule flux tubes tilted with respect to the solar surface
provide a mechanism by which oscillatory power from lower in the
atmosphere may be channeled to upper portions of the atmosphere.  This
suggests that a second model $M_{2}$ for the \Fps\ in regions should
be considered.  The second model $M_{2}$ has two contributions to the
overall \Fps; a background power-law of the form of $P_{1}$, and a
contribution that is more localized, $G(\nu)$.  The model is given by
\begin{equation}
\label{eqn:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\delta^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions (Figure
\ref{fig:fit171193}), and compared to decide which model best
describes the data. The details of the model fitting process are
described in \ref{sec:app:ind}.  The position of $G(\nu)$ is
restricted by permitting $\beta$ to vary in the range $1-10$ mHz only.
This restriction, which is imposed in the fitting process (see Section
\ref{sec:app:ind}), arises from the observations of significant
  wavelet power in the period rangs 200 - 600 seconds as found by
  \cite{2003ApJ...595L..63D}.

@@

\subsection{Model fitting and selection}
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.  A
Bayesian/Markov chain Monte Carlo package (PyMC version 2.3,
\cite{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
the Bayesian posterior and determine model parameter estimates and
their uncertainty.  If $P_{i,j}$ is the power at Fourier frequency
$\nu_{j}$ from Model $i$ then the likelihood $L$ is
\begin{equation}\label{eqn:likelihood}
L = \prod_{j=1}^{N_{f}}
\frac{1}{\sqrt{2\pi\sigma^{2}}}
\exp\left(
-\frac{(P_{i,j} - D_{j})^{2}}{2\sigma_{j}^{2}}
\right)
\end{equation}
where $D_{j}$ is the observed \mFps\ at frequency $\nu_{j}$,
$N_{f}$ is the number of Fourier frequencies, and $\sigma_{j}$ is the
normal distribution width at frequency $\nu_{j}$ .  Each of the priors for
the parameters in each model has a uniform distribution, and are given
in Table \ref{tab:priors}.  Each MCMC chain that was run took 100,000
samples, with burn-in assumed to be at 50,000 samples.  The chain is
thinned by taking every fifth element in the chain, forming the final
sample from which the parameter estimates and their uncertainties are
calculated.
\begin{deluxetable}{ccc}
\tabletypesize{\scriptsize} 
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{Priors for each of the parameters used in Model 1
  (Equation \ref{eqn:pwrlaw}) and
  Model 2 (Equation \ref{eqn:pwrlawbump}) \label{tab:priors}}
\tablehead{
\colhead{parameter} &
\colhead{Model 1} &
\colhead{Model 2} \\
}
\startdata
$A$ & $4.5 \times 10^{-5} \rightarrow 22026$ &  $4.5 \times 10^{-5} \rightarrow 22026$\\
$n$  &  $-1\rightarrow 6$   & $-1\rightarrow 6$  \\
$C$ & $2.1 \times 10^{-9} \rightarrow 22026$  & $2.1 \times 10^{-9} \rightarrow 22026$  \\
$\alpha$  & not applicable & $2.1 \times 10^{-9} \rightarrow 148$ \\
$\beta$ & not applicable  & $0.5 - 10 mHz$ \\
$\delta$ & not applicable & $0.001\rightarrow 3$ decades of frequency\\
\enddata
\end{deluxetable}

@@

\begin{enumerate}
\item The MCMC sampler is run to fit Model 1, assuming $\sigma_{j} =
  \sigma_{original, j}$ the width of the distribution of Fourier power
  at frequency $G(\nu_{j})$.  Since these widths are much larger than
  $\sigma_{mean}$ is much wider than the standard error in the mean,
  it allows the fitting algorithm to converge to an approximate fit
  solution.
\item The MCMC sampler is run to fit Model 1 with $\sigma_{j} =
  \sigma_{mean, j}$, with $\sigma_{mean, j}= \sigma_{original,
    j}/sqrt{N_{eff}}$, seeded with estimated parameter values from
  step 1.  This generates a better estimate to the parameters of the
  model fit.  The resulting parameter estimates are given by the mean
  values of marginal probability distribution functions, and are the
  final estimates for Model 1.
\item The residuals of the model 1 fit to the data are then used to
  estimate the model parameters of $G(\nu)$.  This is done by
  (least-squares) fitting $G(\nu)$ to the positive residuals in the
  frequency range 0.1 - 10 mHz.
\item The MCMC sampler is run to fit Model 1,2 assuming $\sigma_{j} =
  \sigma_{original, j}$, seeded with the mean parameter values of
  Model 1 from step 2 and the estimated $G(\nu)$ model parameters from
  step 3.
\item The MCMC sampler is run to fit Model 2 with $\sigma_{j} =
  \sigma_{mean, j}$, seeded with estimated parameter values from step
  4.  The resulting parameter estimates are given by the mean values
  of marginal probability distribution functions, and are the final
  estimates for Model 2.
\end{enumerate}
Models are selected using the Akaike and Bayesian Information Criteria
\citep{2007MNRAS.377L..74L}.  Conveniently, these quantities are also
calculated by the PyMC package used to perform the MCMC sampling.  The
68\% credible intervals for the parameters are quoted in Table
\ref{tab:parameters}.  The upper and lower limits to the credible
intervals are found by determining the values beyond which 16\% of the
probability lies in each wing of the marginal distributions.

@@
